A Software Engineering Perspective on \\ OpenMP and PThreads

### 2017-08-09 sections/00-abstract.tex
Reviewing abstract

    Selecting the most effective tools and languages for teaching parallel and
    distributed computing presents a challenge for teachers and students. Often
    a high-level solution seems easier, but it comes with the cost of hiding
    underlying concepts and problems. We present a comparison between the
    \textit{Pthreads} and \textit{OpenMP} APIs considering the experiences and
    performance results of undergraduate and graduate Computer Science students
    from the University of São Paulo.
    We show that students were able to achieve better performance results using
    \textit{Pthreads} than \textit{OpenMP}, despite their perception that
    \textit{Pthreads} is harder to learn and use.

>>>>

Selecting the most effective tools and languages for teaching parallel and
distributed computing presents a challenge for teachers and students. Often a
high-level solution seems easier, but it comes with the cost of hiding
underlying concepts and problems. In this paper we present a comparison between
the \textit{Pthreads} and \textit{OpenMP} APIs considering the experiences and
performance results of undergraduate and graduate Computer Science students.
We show that students were able to achieve better performance results using
\textit{Pthreads} than \textit{OpenMP}, despite their perception that
\textit{Pthreads} is harder to learn and use.
